Polymethylation scores paper

### 2021-09-14 Papers/Polymethylation_scores/index_paper.Rmd
wrote methods section: polymethylation scores

---
title: "Polymethylation scores paper"
author: "F blostein"
date: "9/13/2021"
output: pdf_document
---

@@

>>>>

---
title: "Polymethylation scores paper"
author: "F blostein"
date: "9/13/2021"
output: pdf_document
bib: Methylation_SmokingBib.bib
---

@@

```{r child = here::here("Papers", "Polymethylation_scores", "03_keywords.Rmd")}
```

```{r child = here::here("Papers", "Polymethylation_scores", "04_background.Rmd")}
```

```{r child = here::here("Papers", "Polymethylation_scores", "05_results.Rmd")}
```

```{r child = here::here("Papers", "Polymethylation_scores", "06_discussion.Rmd")}
```

```{r child = here::here("Papers", "Polymethylation_scores", "07_conclusions.Rmd")}
```

```{r child = here::here("Papers", "Polymethylation_scores", "98_declarations.Rmd")}
```

# References
